Full Title of Article\titlebreak This Title Has A Line Break

### 2021-08-18 Submission/Paper/ML4H/Paper.tex
section 3 draft

\paragraph{Annotations}
\label{sec:Annotations} We initially assigned 5,000 sequences diversified by keyword matches from 5,000 unique patients for neurologist labeling. As the manual annotation of 279,000+ sequences in not feasible, we devised a scheme to expedite annotations known as "always patterns". An always pattern is defined as a phrase or regex expression that in any context indicates the phrase will be labeled with a particular class (i.e. yes, no, or neither). If an always pattern is inputted, all other sequences have language that matches with the phrase will be automatically labeled accordingly. {List any other sequence assignment schemes}

% The \textsf{jmlr} class loads the \textsf{amsmath} package, so
% you can use any of the commands and environments defined there.
% (See the \textsf{amsmath} documentation for further
% details.\footnote{Either \texttt{texdoc amsmath} or
% \url{http://www.ctan.org/pkg/amsmath}})

% Unnumbered single-lined equations should be displayed using
% \verb|\[| and \verb|\]|. For example:
% \[E = m c^2\]
% or you can use the \texttt{displaymath} environment:
% \begin{displaymath}
% E = m c^2
% \end{displaymath}
% Numbered single-line equations should be displayed using the
% \texttt{equation} environment. For example:
% \begin{equation}\label{eq:trigrule}
% \cos^2\theta + \sin^2\theta \equiv 1
% \end{equation}
% This can be referenced using \verb|\label| and \verb|\equationref|.
% For example, \equationref{eq:trigrule}.

% Multi-lined numbered equations should be displayed using the
% \texttt{align} environment.\footnote{For reasons why you 
% shouldn't use the obsolete \texttt{eqnarray} environment, see
% Lars Madsen, \emph{Avoid eqnarray!} TUGboat 33(1):21--25, 2012.} For example:
% \begin{align}
% f(x) &= x^2 + x\label{eq:f}\\
% f'(x) &= 2x + 1\label{eq:df}
% \end{align}
% Unnumbered multi-lined equations can be displayed using the
% \texttt{align*} environment. For example:
% \begin{align*}
% f(x) &= (x+1)(x-1)\\
% &= x^2 - 1
% \end{align*}
% If you want to mix numbered with unnumbered lines use the
% \texttt{align} environment and suppress unwanted line numbers with
% \verb|\nonumber|. For example:
% \begin{align}
% y &= x^2 + 3x - 2x + 1\nonumber\\
% &= x^2 + x + 1\label{eq:y}
% \end{align}
% An equation that is too long to fit on a single line can be
% displayed using the \texttt{split} environment. 
% Text can be embedded in an equation using \verb|\text| or
% \verb|\intertext| (as used in \theoremref{thm:eigenpow}).
% See the \textsf{amsmath} documentation for further details.

% \subsection{Operator Names}
% \label{sec:op}

% Predefined operator names are listed in \tableref{tab:operatornames}.
% For additional operators, either use \verb|\operatorname|,
% for example $\operatorname{var}(X)$ or declare it with
% \verb|\DeclareMathOperator|, for example
% \begin{verbatim}
% \DeclareMathOperator{\var}{var}
% \end{verbatim}
% and then use this new command. If you want limits that go above and
% below the operator (like \verb|\sum|) use the starred versions
% (\verb|\operatorname*| or \verb|\DeclareMathOperator*|).

% \begin{table*}[htbp]
% \floatconts
%   {tab:operatornames}%
%   {\caption{Predefined Operator Names (taken from 
%   \textsf{amsmath} documentation)}}%
%   {%
% \begin{tabular}{rlrlrlrl}
% \cs{arccos} & $\arccos$ &  \cs{deg} & $\deg$ &  \cs{lg} & $\lg$ &  \cs{projlim} & $\projlim$ \\
% \cs{arcsin} & $\arcsin$ &  \cs{det} & $\det$ &  \cs{lim} & $\lim$ &  \cs{sec} & $\sec$ \\
% \cs{arctan} & $\arctan$ &  \cs{dim} & $\dim$ &  \cs{liminf} & $\liminf$ &  \cs{sin} & $\sin$ \\
% \cs{arg} & $\arg$ &  \cs{exp} & $\exp$ &  \cs{limsup} & $\limsup$ &  \cs{sinh} & $\sinh$ \\
% \cs{cos} & $\cos$ &  \cs{gcd} & $\gcd$ &  \cs{ln} & $\ln$ &  \cs{sup} & $\sup$ \\
% \cs{cosh} & $\cosh$ &  \cs{hom} & $\hom$ &  \cs{log} & $\log$ &  \cs{tan} & $\tan$ \\
% \cs{cot} & $\cot$ &  \cs{inf} & $\inf$ &  \cs{max} & $\max$ &  \cs{tanh} & $\tanh$ \\
% \cs{coth} & $\coth$ &  \cs{injlim} & $\injlim$ &  \cs{min} & $\min$ \\
% \cs{csc} & $\csc$ &  \cs{ker} & $\ker$ &  \cs{Pr} & $\Pr$
% \end{tabular}\par
% \begin{tabular}{rlrl}
% \cs{varlimsup} & $\varlimsup$ 
% & \cs{varinjlim} & $\varinjlim$\\
% \cs{varliminf} & $\varliminf$ 
% & \cs{varprojlim} & $\varprojlim$
% \end{tabular}
% }
% \end{table*}

\section{Vectors and Sets}
\label{sec:vec}

Vectors should be typeset using \cs{vec}. For example $\vec{x}$.
(The original version of \cs{vec} can also be accessed using
\cs{orgvec}, for example $\orgvec{x}$.)
The \textsf{jmlr} class also provides \cs{set} to typeset a
set. For example $\set{S}$.

\section{Floats}
\label{sec:floats}

Floats, such as figures, tables and algorithms, are moving
objects and are supposed to float to the nearest convenient
location. Please don't force them to go in a particular place. In
general it's best to use the \texttt{htbp} specifier and don't
put the figure or table in the middle of a paragraph (that is
make sure there's a paragraph break above and below the float).
Floats are supposed to have a little extra space above and below
them to make them stand out from the rest of the text. This extra
spacing is put in automatically and shouldn't need modifying.

If your article will later be reprinted in the Challenges for
Machine Learning, please be aware that the CiML books use a
different paper size, so if you want to resize any images use a
scale relative to the line width (\verb|\linewidth|), text width
(\verb|\textwidth|) or text height (\verb|\textheight|).

To ensure consistency, please \emph{don't} try changing the format of the caption by doing
something like:
\begin{verbatim}
\caption{\textit{A Sample Caption.}}
\end{verbatim}
or
\begin{verbatim}
\caption{\em A Sample Caption.}
\end{verbatim}
You can, of course, change the font for individual words or 
phrases, for example:
\begin{verbatim}
\caption{A Sample Caption With Some \emph{Emphasized Words}.}
\end{verbatim}

\subsection{Tables}
\label{sec:tables}

Tables should go in the \texttt{table} environment. Within this
environment use \verb|\floatconts| (defined by \textsf{jmlr})
to set the caption correctly and center the table contents.
The location of the caption depends on the \verb|tablecaption|
setting in the document class options.

\begin{table}[htbp]
 % The first argument is the label.
 % The caption goes in the second argument, and the table contents
 % go in the third argument.
\floatconts
  {tab:example}%
  {\caption{An Example Table}}%
  {\begin{tabular}{ll}
  \bfseries Dataset & \bfseries Result\\
  Data1 & 0.12345\\
  Data2 & 0.67890\\
  Data3 & 0.54321\\
  Data4 & 0.09876
  \end{tabular}}
\end{table}

If you want horizontal rules you can use the \textsf{booktabs}
package which provides the commands \verb|\toprule|, 
\verb|\midrule| and \verb|\bottomrule|. For example, see
\tableref{tab:example-booktabs}.

\begin{table}[hbtp]
\floatconts
  {tab:example-booktabs}
  {\caption{A Table With Horizontal Lines}}
  {\begin{tabular}{ll}
  \toprule
  \bfseries Dataset & \bfseries Result\\
  \midrule
  Data1 & 0.12345\\
  Data2 & 0.67890\\
  Data3 & 0.54321\\
  Data4 & 0.09876\\
  \bottomrule
  \end{tabular}}
\end{table}

If you really want vertical lines as well, you can't use the
\textsf{booktabs} commands as there'll be some unwanted gaps.
Instead you can use \LaTeX's \verb|\hline|, but the rows may
appear a bit cramped.  You can add extra space above or below a
row using \verb|\abovestrut| and \verb|\belowstrut|. For example,
see \tableref{tab:example-hline}. However, you might want to read
the \textsf{booktabs} documentation regarding the use of vertical
lines.

\begin{table}[htbp]
\floatconts
  {tab:example-hline}
  {\caption{A Table With Horizontal and Vertical Lines}}%
  {%
    \begin{tabular}{|l|l|}
    \hline
    \abovestrut{2.2ex}\bfseries Dataset & \bfseries Result\\\hline
    \abovestrut{2.2ex}Data1 & 0.12345\\
    Data2 & 0.67890\\
    Data3 & 0.54321\\
    \belowstrut{0.2ex}Data4 & 0.09876\\\hline
    \end{tabular}
  }
\end{table}

If you want to align numbers on their decimal point, you can
use the \textsf{siunitx} package. For example, see
\tableref{tab:example-siunitx}. For further details see the
\textsf{siunitx} documentation\footnote{Either \texttt{texdoc
siunitx} or \url{http://www.ctan.org/pkg/siunitx}}.

\begin{table}[htbp]
\floatconts
  {tab:example-siunitx}
  {\caption{A Table With Numbers Aligned on the Decimal Point}}
  {\begin{tabular}{lS[tabformat=3.5]}
  \bfseries Dataset & {\bfseries Result}\\
  Data1 & 0.12345\\
  Data2 & 10.6789\\
  Data3 & 50.543\\
  Data4 & 200.09876
  \end{tabular}}
\end{table}

If the table is too wide, you can adjust the inter-column
spacing by changing the value of \verb|\tabcolsep|. For
example:
\begin{verbatim}
\setlength{\tabcolsep}{3pt}
\end{verbatim}
If the table is very wide but not very long, you can use the
\texttt{sidewaystable} environment defined in the
\textsf{rotating} package (so use \verb|\usepackage{rotating}|).
If the table is too long to fit on a page, you can use the
\texttt{longtable} environment defined in the \textsf{longtable}
package (so use \verb|\usepackage{longtable}|).

\subsection{Figures}
\label{sec:figures}

Figures should go in the \texttt{figure} environment. Within this
environment, use \verb|\floatconts| to correctly position the
caption and center the image. Use \verb|\includegraphics|
for external graphics files but omit the file extension. Do not
use \verb|\epsfig| or \verb|\psfig|. If you want to scale the
image, it's better to use a fraction of the line width rather
than an explicit length. For example, see \figureref{fig:nodes}.

\begin{figure}[htbp]
 % Caption and label go in the first argument and the figure contents
 % go in the second argument
\floatconts
  {fig:nodes}
  {\caption{Example Image}}
  {\includegraphics[width=0.5\linewidth]{images/nodes}}
\end{figure}

If your image is made up of \LaTeX\ code (for example, commands
provided by the \textsf{pgf} package) you can include it using
\cs{includeteximage} (defined by the \textsf{jmlr} class). This
can be scaled and rotated in the same way as \cs{includegraphics}.
For example, see \figureref{fig:teximage}.

\begin{figure}[htbp]
\floatconts
  {fig:teximage}
  {\caption{Image Created Using \LaTeX\ Code}}
  {\includeteximage[angle=45]{images/teximage}}
\end{figure}

If the figure is too wide to fit on the page, you can use the
\texttt{sidewaysfigure} environment defined in the
\textsf{rotating} package.

Don't use \verb|\graphicspath|.\footnote{This is specific to the
\textsf{jmlr} class, not a general recommendation. The main file
that generates the proceedings or the CiML book is typically in a
different directory to the imported articles, so it modifies the
graphics path when it imports an article.} If the images 
are contained in a subdirectory, specify this when you include the image, for
example \verb|\includegraphics{figures/mypic}|.

\subsubsection{Sub-Figures}
\label{sec:subfigures}

Sub-figures can be created using \verb|\subfigure|, which is
defined by the \textsf{jmlr} class. The optional argument allows
you to provide a subcaption. The label should be placed in the
mandatory argument of \verb|\subfigure|. You can reference the
entire figure, for example \figureref{fig:subfigex}, or you can
reference part of the figure using \verb|\figureref|, for example
\figureref{fig:circle}. Alternatively you can reference the
subfigure using \verb|\subfigref|, for example
\subfigref{fig:circle,fig:square} in \figureref{fig:subfigex}.

\begin{figure}[htbp]
\floatconts
  {fig:subfigex}
  {\caption{An Example With Sub-Figures.}}
  {%
    \subfigure[A Circle]{\label{fig:circle}%
      \includegraphics[width=0.2\linewidth]{images/circle}}%
    \qquad
    \subfigure[A Square]{\label{fig:square}%
      \includegraphics[width=0.2\linewidth]{images/square}}
  }
\end{figure}

By default, the sub-figures are aligned on the baseline.
This can be changed using the second optional argument
of \verb|\subfigure|. This may be \texttt{t} (top), \texttt{c}
(centered) or \texttt{b} (bottom). For example, the subfigures
\subfigref{fig:circle2,fig:square2} in \figureref{fig:subfigex2}
both have \verb|[c]| as the second optional argument.

\begin{figure}[htbp]
\floatconts
  {fig:subfigex2}
  {\caption{Another Example With Sub-Figures.}}
  {%
    \subfigure[A Small Circle][c]{\label{fig:circle2}%
      \includegraphics[width=0.1\linewidth]{images/circle}}%
    \qquad
    \subfigure[A Square][c]{\label{fig:square2}%
      \includegraphics[width=0.2\linewidth]{images/square}}
  }
\end{figure}

\subsection{Sub-Tables}
\label{sec:subtables}
There is an analogous command \verb|\subtable| for sub-tables.
It has the same syntax as \verb|\subfigure| described above.
You can reference the table using \verb|\tableref|, for example
\tableref{tab:subtabex} or you can reference part of the table,
for example \tableref{tab:ab}. Alternatively you can reference the
subtable using \verb|\subtabref|, for example
\subtabref{tab:ab,tab:cd} in \tableref{tab:subtabex}.

\begin{table}[htbp]
\floatconts
 {tab:subtabex}
 {\caption{An Example With Sub-Tables}}
 {%
   \subtable{%
     \label{tab:ab}%
     \begin{tabular}{cc}
     \bfseries A & \bfseries B\\
     1 & 2
     \end{tabular}
   }\qquad
   \subtable{%
     \label{tab:cd}%
     \begin{tabular}{cc}
     \bfseries C & \bfseries D\\
     3 & 4\\
     5 & 6
     \end{tabular}
   }
 }
\end{table}

By default, the sub-tables are aligned on the top.
This can be changed using the second optional argument
of \verb|\subtable|. This may be \texttt{t} (top), \texttt{c}
(centered) or \texttt{b} (bottom). For example, the sub-tables
\subtabref{tab:ab2,tab:cd2} in \tableref{tab:subtabex2}
both have \verb|[c]| as the second optional argument.

\begin{table}[htbp]
\floatconts
 {tab:subtabex2}
 {\caption{Another Example With Sub-Tables}}
 {%
   \subtable[][c]{%
     \label{tab:ab2}%
     \begin{tabular}{cc}
     \bfseries A & \bfseries B\\
     1 & 2
     \end{tabular}
   }\qquad
   \subtable[][c]{%
     \label{tab:cd2}%
     \begin{tabular}{cc}
     \bfseries C & \bfseries D\\
     3 & 4\\
     5 & 6
     \end{tabular}
   }
 }
\end{table}

>>>>

\paragraph{Annotations}
\label{sec:Annotations} We initially assigned 5,000 sequences diversified by keyword matches from 5,000 unique patients for neurologist labeling. As the manual annotation of 279,000+ sequences in not feasible, we devised a scheme to expedite annotations known as "always patterns". An always pattern is defined as a phrase or regex expression that in any context indicates the phrase will be labeled with a particular class (i.e. yes, no, or neither). If an always pattern is inputted, all other sequences have language that matches with the phrase will be automatically labeled accordingly. % {List any other sequence assignment schemes} %
Currently, 8,656 sequences have been annotated, 8,050 through always patterns and 606 manually. % {Will change} %

The final dataset was split between train (95\%) and holdout test (5\%) sets, stratified across label and proportion of sequences annotated manually and through always patterns. % {Will change} % 
Validation datsets were split from the train set using techniques described in the Methodology section. Table 2 shows demographics of the cohort of patients.

\section{Methodology}
\label{sec:Methodology}

We built x models and compared performance to baseline model.

\paragraph{(1) Structured Features Model}

\paragraph{(2) Logistic Regression with TF-IDF Vectors}

\paragraph{(3) Model 1 + Model 2}

\paragraph{(4) Transformer Based Sequence Classification Language Model}
